VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-05-12 snapshot_system/paper_del.tex
updates to contributions

Snapshot deletions can occur frequently since old snapshots become less useful.
General deduplication complicates the deletion process because sharing of duplicates
requires a global reference counting~\cite{Guo2011,Fabiano2013} 
 to identify if  a chunk can be  safely removed without any reference.
%The complexity of our distributed environment obviates reference counting as an option,
%and While we can use the mark-and-sweep, 
%While the mark-and-sweep techniques can be used and optimization can be considered~\cite{Fabiano2013},
%it still takes significant resources to conduct reference counting every time there is a snapshot deletion.
%
%In the case of Alibaba, snapshot backup is conducted automatically and there are 
%about 10 snapshot stored for every VM customer.
% Snapshot deletion can occur frequently, for example when there is
% a new snapshot created every day,  there will usually be a snapshot expired every day to maintain
% balanced storage use. 
%In addition, cloud users expect the reduced storage usage to be reflected
%instantly, which makes it difficult to adopt some resource efficient techniques such like perfect hashing\cite{Fabiano2013}.
Since our VM-centric design restricts sharing of data chunks only to a small dataset,
we can greatly simplify the deletion process by 
focusing on  unreferenced non-PDS chunks within each VM. 
This process can be conducted independently per VM, and thus results in  a simpler flow control and 
lower resource usage. 
%The PDS data chunks are commonly shared among all VMs and we do not consider them
%during snapshot deletion.  The selection of PDS data chunks is updated periodically independent of snapshot deletion process.

We further propose an {\em approximate} deletion strategy to trade deletion accuracy for
speed and resource usage. Our method sacrifices a small percent of storage leakage
to efficiently identify unused chunks.
The algorithm contains three aspects.
\begin{itemize}
\item {\bf Computation for snapshot reference summary.}
Every time there is a new snapshot created,
we compute a Bloom-filter with $z$ bits as the reference summary vector for all non-PDS chunks used 
in this snapshot.
The items we put into the summary vector are all the references appearing in the metadata of the snapshot.
For each VM we preset the vector size according to estimated VM image size;
given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
We adjust the summary vector size and recompute the vectors if the VM size changes substantially over time.
This can be done during periodic leakage repair described below.

>>>>

Snapshot deletions can occur frequently since old snapshots become less useful.
General deduplication complicates the deletion process because sharing of duplicates
requires a global reference counting~\cite{Guo2011,Fabiano2013} 
 to identify if  a chunk can be  safely removed without any reference.
%Since our VM-centric design restricts sharing of data chunks only to a small dataset,
%we can greatly simplify the deletion process by 
%focusing on  unreferenced non-PDS chunks within each VM. 
%This process can be conducted independently per VM, and thus results in  a simpler flow control and 
%lower resource usage. 
One of the key benefits of our VM-centric design is that it allows for faster and simpler deletion. First, since
sharing in our approach is limited to only a small dataset, we can greatly simplify deletion by focusing
on intra-VM sharing rather than inter-VM sharing. Our deletion can therefore be conducted independently per VM.
Second, we propose an {\em approximate} deletion stragegy to trade deletion accuracy for speed and
resource usage.

Our approximate deletion method sacrifices a small percent of storage leakage
to efficiently identify unused chunks using a per-snapshot bloomfilter.
The algorithm contains three aspects.
\begin{itemize}
\item {\bf Computation for snapshot reference summary.}
Every time there is a new snapshot created,
we compute a Bloom-filter with $z$ bits as the reference summary vector for all non-PDS chunks used 
in this snapshot.
The items we put into the summary vector are all the references appearing in the metadata of the snapshot.
For each VM we preset the vector size according to estimated VM image size;
given $h$ snapshots stored for a VM, there are $h$ summary vectors maintained.
We adjust the summary vector size and recompute the vectors if the VM size changes substantially over time.
This can be done during periodic leakage repair described below.

### 2014-05-12 snapshot_system/paper_intro.tex
updates to contributions

This paper considers a backup service for converged cloud architectures
that is co-located with user VMs, sharing the cloud computer, network, and
storage resource with them.
We describe methodologies to address the following two challenges: 
1) simple deduplication and snapshot deletion with competitive efficiency and 
a small resource usage without affecting other collocated cloud services;
2) improved fault isolation for the sharing of deduplicated data,
given that node failures in converged architecture are the norm rather than
exception. 
% so that users stop incurring storage charges immediately after snapshot deletion.
%\end{itemize}

>>>>

This paper considers a backup service for converged cloud architectures
that is co-located with user VMs, sharing the cloud compute, network, and
storage resources with them.
%We describe methodologies to address the following two challenges: 
The key contribution of this work is a set of methodologies to address the following two challenges:
1) simple deduplication and snapshot deletion with competitive efficiency and 
a small resource usage without affecting other collocated cloud services;
2) improved fault isolation for the sharing of deduplicated data,
given that node failures in converged architecture are the norm rather than
exception. 
% so that users stop incurring storage charges immediately after snapshot deletion.
%\end{itemize}
